Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-05-24 cvx-flats-neurips21/cvx-flats.tex
typo

\begin{corollary}
  \label{cor:spectral-risks}
  Let $\P$ be a set of continuous Lebesgue densities on $\Y=\reals$ with all $p \in \P$ having support on the same interval.
  If we have $p_1,p_2,p_3,p_2'\in\P$ with $q_\alpha(p_1) < q_\alpha(p_2) < q_\alpha(p_3)$ and $\CVaR_\alpha(p_2) \neq \CVaR_\alpha(p_2')$,
  then $\conscvx(\CVaR_\alpha) \geq \eliccvx(\CVaR_\alpha) \geq 2$.
\end{corollary}
As first shown by \citet{fissler2016higher}, the pair $(\CVaR_\alpha,q_\alpha)$ is jointly indentifiable and elicitable, but not by any convex loss~\citep[Prop.\ 4.2.31]{fissler2017higher}.
We conjecture the stronger statement $\eliccvx(\CVaR_\alpha) \geq 3$, which if true would constitute an interesting gap between elicitation complexity for identifiable and convex-elicitable properties.

>>>>

\begin{corollary}
  \label{cor:spectral-risks}
  Let $\P$ be a set of continuous Lebesgue densities on $\Y=\reals$ with all $p \in \P$ having support on the same interval.
  If we have $p_1,p_2,p_3,p_2'\in\P$ with $q_\alpha(p_1) < q_\alpha(p_2) < q_\alpha(p_3)$ and $\CVaR_\alpha(p_2) \neq \CVaR_\alpha(p_2')$,
  then $\conscvx(\CVaR_\alpha) \geq \eliccvx(\CVaR_\alpha) \geq 2$.
\end{corollary}
As first shown by \citet{fissler2016higher}, the pair $(\CVaR_\alpha,q_\alpha)$ is jointly identifiable and elicitable, but not by any convex loss~\citep[Prop.\ 4.2.31]{fissler2017higher}.
We conjecture the stronger statement $\eliccvx(\CVaR_\alpha) \geq 3$, which if true would constitute an interesting gap between elicitation complexity for identifiable and convex-elicitable properties.
